Characterization of gaps in directly bonded Si compound optics

### 2014-10-22 AO_bondedSi.tex
closes #20- Overhaul Table 3 to reflect marked-up paper draft, Table 3 is summary of Cary5000 measurement parameters

\begin{table}[h!]
\caption{Summary of Cary 5000 Measurement parameters \label{tab:Cary5000pars}}
\begin{center}
\begin{tabular}{ c c }
\hline
        Parameter (Units) & Value \\ 
\hline
        Spectral sampling interval (nm) & 2.0$-$10.0 \\
        Spectral resolution (nm) & 5 \\
        Time per sample (s) & 0.1 \\
        Available measurement range (nm) & 175-3300 \\
        Typical measurement range (nm) & 1000-2500 \\
	Single mode RMS  (\%) & 0.02 \\
	Double mode RMS  (\%) & 0.002 \\
	Typical Single mode mean drift (\%) & 0.20 \\
	Typical Double mode mean drift (\%) & 0.02 \\
	No beam dark signal (\%) & 0.03 \\
 	Beam size (mm $\times$ mm) & $2 \times 8$ \\
	Wavelengths of instrumental artifacts (nm) & - \\
        		 & 1200 \\
		 & 1350 \\
		 & 1360-1450\\
		 & 1850 \\
		 & 1800-1950 \\
		 & 2000 \\
        Vendor-reported linearity range (dB) & $>40$ \\
        Directly measured linearity range (dB) & $>24$ \\
    \hline
    \end{tabular}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\caption{Summary of Cary 5000 Measurement parameters \label{tab:Cary5000pars}}
\begin{center}
\begin{tabular}{ c c }
\hline
        Parameter (Units) & Value \\ 
\hline
        Spectral sampling interval (nm) & 2.0$-$10.0 \\
        Spectral resolution (nm) & 5 \\
        Time per sample (s) & 0.1 \\
        Typical measurement range (nm) & 1000-2500 \\
	Typical Single mode mean drift (\%) & 0.20 \\
 	Beam size (mm $\times$ mm) & $2 \times 8$ \\
        Directly measured linearity range (dB) & $>24$ \\
    \hline
    \end{tabular}
\end{center}
\end{table}
